|

### 2024-08-11 doc/presentation.qmd
presentation workflow

import pickle

with open('../output/results.pickle', 'rb') as f:
        results = pickle.load(f)

min_fyear, max_fyear, no_unique_firms = results['Desc information'].values()

def rename_var_to_label(table, italic=True):
    for var_name, var_label in results['Variable Names'].items():
        var_label = f'\\textit{{{var_label}}}' if italic else var_label
        table = table.replace(var_name, var_label)
    return table
```

\pagebreak

@@

### Discretionary Accruals

@@

### Data

```{python}
#| echo: false
#| output: asis

lat_tab = rename_var_to_label(results['Descriptive Statistics']).split('\n')
# lat_tab[4] = '\\\\[-1.8ex]\\hline \\hline \\\\[-1.8ex]'
# lat_tab[6] = '\\hline\\\\[-1.8ex]'
# lat_tab[-4] = '\\\\[-1.8ex]\\hline \\hline \\\\[-1.8ex]'

print('\n'.join([
    '\\begin{table}[!htbp]',  
    '\\resizebox{\\textheight}{!}{',
    '\\begin{threeparttable}',
    '\n'.join(lat_tab[3:-2]),
    '\\begin{tablenotes}[flushleft]',
    '\setlength{\labelsep}{0pt}',
    f'\\item Note: The data is obtained from the Compustat U.S. as provided by WRDS. The sample covers the period {int(min_fyear)} to {int(max_fyear)} and {no_unique_firms:,} unique firms.',
    '\end{tablenotes}',
    '\end{threeparttable}',
    '}',
    '\\end{table}',
]))
```

### Distribution of Discretionary Accruals over time - unrestricted sample

```{python}
#| label: fig-boxplot_full
#| fig-cap: "Distribution of Discretionary Accruals over time - unrestricted sample"
#| echo: false
results['fig_boxplot_full'].set_figheight(2.6)
results['fig_boxplot_full']
```

### Distribution of Discretionary Accruals over time - analysis sample

```{python}
#| label: fig-boxplot_smp
#| fig-cap: "Distribution of Discretionary Accruals over Time - analysis sample"
#| echo: false
results['fig_boxplot_smp'].set_figheight(2.6)
results['fig_boxplot_smp']
```

### Correlation of Modified Jones with Dechow and Dichev DA

```{python}
#| label: fig-scatter_md_dd
#| fig-cap: "Correlation of Modified Jones with Dechow and Dichev DA"
#| echo: false
results['fig_scatter_md_dd'].set_figheight(3)
results['fig_scatter_md_dd']
```

### Association of Dechow and Dichev DA with firm size

```{python}
#| label: fig-scatter_dd_lnta
#| fig-cap: "Dechow and Dichev DA and Firm Size"
#| echo: false

results['fig_scatter_dd_lnta'].set_figheight(3)
results['fig_scatter_dd_lnta']
```

### No presentation without correlation table...

```{python}
#| echo: false
#| output: asis

lat_tab = rename_var_to_label(results['Correlations'], False).split('\n')
lat_tab[2] = '\\\\[-1.8ex]\\hline \\hline \\\\[-1.8ex]'
lat_tab[4] = '\\hline\\\\[-1.8ex]'
lat_tab[-7] = '\\\\[-1.8ex]\\hline \\hline \\\\[-1.8ex]'

print('\n'.join([
    '\\begin{center}',
    '\\resizebox*{\\textwidth}{!}{',
    '\\begin{tabular}{lccccccc}',
    '\n'.join(lat_tab[2:-6]),
    '\\end{tabular}}',
    '\\end{center}'
]))
```

### ... and regression table

```{python}
#| echo: false
#| output: asis

print('\n'.join([
    '\\begin{center}',
    '\\resizebox*{!}{0.8\\textheight}{', 
    '\\begin{tabular}{lcc}',
    rename_var_to_label('\n'.join(results['Regression'].split('\n')[4:-2])),
    '\\end{tabular}}',
    '\\end{center}'
]))
```

@@

- Discretionary accruals are simply wonderful! 
- With these distributional properties and the power of large samples they will almost always be significant in one direction or the other regardless the setting or controls
- Use them for every economic construct under the sun!

>>>>

import pickle
import pandas as pd

# Load the results from the existing pickle file for table_1
with open('../data/generated/table_1.pickle', 'rb') as f:
    results = pickle.load(f)

# Load the results from the new pickle file for final_table and summary_stats
with open('../output/em_results.pickle', 'rb') as f:
    em_results = pickle.load(f)

def escape_special_characters(df):
    df.columns = [col.replace('_', '\\_').replace('#', '\\#') for col in df.columns]
    return df

# Custom formatter function
def custom_float_format(x):
    return f"{x:.3f}".lstrip('0') if pd.notnull(x) else ""

def prep_latex_table(df, caption=None, label=None, fontsize='\\fontsize{11}{13}\\selectfont', description=None):
    df = escape_special_characters(df.reset_index(drop=True))  # Drop the index column from output tables for better readability
    num_columns = len(df.columns)
    column_format = 'l' + 'r' * (num_columns - 1)

    latex_table = df.to_latex(
        column_format=column_format,
        index=False, 
        float_format=custom_float_format,
        escape=False  # Important to disable escaping so LaTeX commands in column names are respected
    )

    # Construct description to the table
    full_caption = f"{caption}\\\\\n\\textnormal{{{description}}}" if description else caption

    latex_table_lines = [
        "\\begin{table}[htbp]",
        "\\centering",
        fontsize,  # Set font size for the table
        latex_table,
        f"\\caption{{{full_caption}}}" if full_caption else "",
        f"\\label{{{label}}}" if label else "",
        "\\end{table}"
    ]
    return "\n".join(line for line in latex_table_lines if line)
```

@@

## Understanding Systematic Differences in Earnings Management across Countries

- The paper of @Leuz_2003 focuses on the relationship between investor protection and earnings management.
- Investor protection plays a crucial role in limiting the extent of earnings management by reducing the opportunities for managers to manipulate earnings.
- Analyzing the relationship between EM and investor protection across different countries provides insights into how legal and institutional frameworks impact financial reporting practices.
- Earnings management (EM) measures reflect the extent to which managers manipulate financial reports to meet certain objectives, such as meeting earnings targets or influencing stock prices.

## Project Objective

- The primary objective is to demonstrate a reproducible and collaborative research workflow by calculating and analyzing EM measures across different countries.
- The study aims to replicate and extend the findings of @Leuz_2003, exploring the relationship between EM and investor protection using Worldscope datasets for the time range 1990 to 1999.
- The analysis provides insights into the levels of earnings management across countries, comparing them with the original findings of Leuz, Nanda, and Wysocki (2003).

## Project Relevance

- Understanding EM trends across countries aids in assessing global financial transparency.
- Promotes transparency and reproducibility in empirical accounting research.

# Research Design

- Data sourced from the Worldscope Database (1990-1999) July 2024 version.
- Replication includes calculation of **four earnings management measures**:
  1. Earnings smoothing using accruals (EM1)
  2. Correlation between changes in accruals and cash flows (EM2)
  3. Magnitude of accruals (EM3)
  4. Ratio of small profits to small losses (EM4)

# Assumptions

- **Database Version**: Analysis uses the July 2024 Worldscope data, which may differ from the November 2000 version due to updates and restatements.
- **Key Terms**: Earnings management (EM) and investor protection defined as per @Leuz_2003 for consistency.
- **Handling Negative Values**: Negative values in key metrics (e.g., operating income) were included to capture the full scope of EM activities.
- **Variable Selection**: Chose specific Worldscope variables (e.g., item1151 over item4051) based on best practices; differences may affect results.
- **Currency Consistency**: EM measures are based on scaled variables; currency consistency ensures comparability across countries.

### Discretionary Accruals ##delete

@@

### Data - Replication Steps

Step 1: Pulling the Data and Managing the Databases

Step 2: Data Preparation

+  To verify the robustness of descriptive statistics before the main replication, Table 1 from Leuz et al. was replicated, yielding results that closely align with the original study:
```{python}
#| label: table_1 
#| echo: false
#| output: asis

print(prep_latex_table(
    results['table_1'],
    caption='Replicated table - Descriptive statistics: Number of firm-year observations per country',
    label='tab:table_1'
))
```

@@

- Significant differences in earnings management practices across countries.
- Strong alignment with original findings in Leuz, Nanda, and Wysocki (2003).
- **Future Work**: Repository can be cloned or forked for further analysis.

# References {-}
\setlength{\parindent}{-0.2in}
\setlength{\leftskip}{0.2in}
\setlength{\parskip}{8pt}
\noindent
